基于卷积神经网络的视频目标跟踪算法研究

### 2021-02-10 博士/毕业论文/ucasthesis/Tex/Frontmatter.tex
写英文摘要

This paper is a help documentation for the \LaTeX{} class ucasthesis, which is  a thesis template for the University of Chinese Academy of Sciences. The main content is about how to use the ucasthesis, as well as how to write thesis efficiently by using \LaTeX{}.

\KEYWORDS{University of Chinese Academy of Sciences (UCAS), Thesis, \LaTeX{} Template}% 英文关键词
%---------------------------------------------------------------------------%

>>>>

Target tracking is one of the most important and challenging research topics in the field of computer vision, and it has potential and broad application prospects in the fields of intelligent surveillance and autonomous driving. The core of target tracking is to estimate the motion state of the target in each frame of the image sequence. Target tracking is the middle part of the computer vision field, which provides a basis for the understanding of target behavior, so it has very important theoretical research value. At the same time, it has a wide range of practical applications, including video surveillance, traffic flow monitoring, video compression, and human-computer interaction. For example, target tracking has been successfully applied to monitor human activities in residential areas, parking lots and banks (such as the W4 system [1] and the VSAM project [2]). In the field of transportation, target tracking is also widely used in traffic flow monitoring [3], pedestrian counting [4] and other tasks.
Due to the theoretical value and application value of target tracking, many scientific research institutions and companies have invested in this research. However, there are many theoretical and technical problems to be solved in the field of target tracking, such as motion blur, illumination changes, deformation of non-rigid targets, target rotation and occlusion caused by changes in viewing angle. In recent years, the breakthrough of deep learning has brought the possibility to solve a series of problems in target tracking.
Deep learning is a machine learning method based on artificial neural networks. In the past ten years, deep learning technology has been rapidly developed and has been successfully applied in computer vision, speech recognition, natural language processing, audio recognition, social network filtering, machine translation, bioinformatics, drug design and other fields. How to use deep learning methods, especially deep convolutional neural networks to solve the complex problems encountered in the tracking process, has great research value and research space.

This paper uses the powerful representation ability of convolutional neural network to improve the feature representation of video target tracking algorithm, appearance model modeling, motion model modeling, model update, etc., and effectively improve the performance of the algorithm. The main work and contributions are:

\begin{itemize}
\item{\textbf{ proposed a semantic information guided video target tracking algorithm. }We use the convolutional neural network to obtain the target \textbf{semantic information} to constrain the training process of the tracker, thereby improving the tracking effect. Specifically, first: We propose an example-guided correlation filter. Use the neural network to learn the instance-level semantic segmentation template of the image to constrain the learning of related filters. Secondly, in view of the complementarity between the semantic segmentation results of offline training and the correlation filtering results of online learning, we propose a self-correction mechanism for tracking results, using the segmentation results to correct the correlation filtering results. We have verified the effectiveness of these innovations in video target tracking applications on multiple challenging video target tracking databases. }
\item{\textbf{ proposed a video target tracking algorithm with enhanced spatial information. }Different from previous work, where the spatial search is done locally to determine the target location, we have introduced richer \textbf{spatial information}. Specifically, the tracking algorithm is optimized in terms of the motion model, and always perceives the position information of the object in the entire image plane, making up for the shortcomings of the limited target search range in the traditional local search mechanism, thereby effectively reducing the accumulated error and improving the robustness. Awesome. In order to further reduce the interference of similar objects, we propose an end-to-end training trajectory prediction module that can use the historical trajectory information of the object and the apparent information of the current frame to predict the possibility of the object appearing in each spatial position of the current frame . We verified the effectiveness of these innovations on multiple video tracking standard evaluation libraries, and greatly improved the accuracy and robustness of the tracking algorithm. }
\item{\textbf{ proposed a video target tracking algorithm enhanced by time information. } The algorithm mainly optimizes the video target tracking algorithm based on the twin network in feature extraction. First, we start from the problem of insufficient robustness of the online video tracking algorithm based on the twin network, and introduce \textbf{time information} into online video target tracking. Through the aggregation of the target appearance information from adjacent frames, the target appearance feature is enriched, and the video target tracking algorithm based on the twin network is limited to extracting the target appearance from a single frame, and thus the lack of ability to express the target appearance , Thereby improving the tracking effect and achieving robust tracking. On the basis of end-to-end time aggregation, we introduced an adversarial dropout module, and through end-to-end training on large-scale data sets, the Siamese network tracker can be used in situations where the target's appearance is not good due to motion blur, etc. Has better performance, thereby further improving the robustness of tracking. We have conducted algorithm comparison experiments and component analysis experiments on the currently popular video target tracking evaluation library to verify the effectiveness of the algorithm improvement. }
\item{\textbf{Propose an adaptive information-enhanced video target tracking algorithm} This algorithm mainly optimizes the video target tracking algorithm based on the twin network in the aspect of model adaptation. We introduced \textbf{adaptive information}. Previous work: offline training. Purpose: Improve the adaptive ability of the algorithm to specific objects. First, by slightly disturbing the pixels of the template image, the tracking performance of the twin network tracker for specific targets is improved. The adaptive information is obtained by back-propagating the gradient of the template image, and can be easily added to the existing twin network tracker in a pluggable manner without modifying the parameters of the network model. In online tracking, only a few times of gradient propagation and template image pixel value update are performed in the first frame to realize the fact tracking of the target. We also verified the effectiveness of the algorithm on multiple video target tracking evaluation libraries, and achieved good results in accuracy and real-time performance. }
\item{\textbf{Applying adversarial information to a video target tracking algorithm based on the Siamese network} We introduced \textbf{adversarial information} and proposed an adversarial attack algorithm. The purpose: to prove the robustness of the existing tracker Sex is not good. Specifically, we generate video-independent general disturbances for the video target tracking algorithm based on the twin network, which makes the tracker behave incorrectly. We add a small perturbation to the template image and a small patch to the search image so that the tracker predicts the location of the patch instead of the location of the target. Through the offline large-scale video target tracking data set training adversarial disturbance information, so as to achieve effective attacks. We verified the effectiveness of the proposed adversarial information on multiple video target tracking standard evaluation libraries, and at the same time verified its transferability in different backbone networks and different tracking frameworks. }
\end{itemize}

\KEYWORDS{Correlation Filter, Visual Object Tracking, Deep Learning, Conlvolutional Neural Network}% 英文关键词
%---------------------------------------------------------------------------%
